---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# metafun

<!-- badges: start -->
<!-- badges: end -->

metafun provides useful functions to teach and understand statistical concept related to Meta-Analyses.

## Installation

You can install the development version of metafun from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("simschaefer/metafun")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(metafun)
## basic example code
```

## Simulate Fixed-Effects model

Simulates data of multiple studies using predefined effect sizes and between study heterogenity ($\tau$).

```{r}
sim <- sim_meta(min_obs = 20,
         max_obs = 2000,
         n_studies = 1500,
         es_true = 0.7,
         es = 'SMD',
         fixed = TRUE,
         random = FALSE,
         varnames = c('x', 'y'))

head(sim$data_aggr)
```
# Effect size and standard error

```{r}
require(tidyverse)

ggplot(sim$data_aggr, aes(x = hedges_g, y = log(se), color = n_x))+
  geom_point(alpha = 0.5)+
  theme_minimal()+
  labs(x = "Effect Size (ES)",
       y = "log(SE)")+
  scale_color_viridis_c()
```
# Run Meta-Analysis

```{r}
require(meta)

metaanalysis <- metagen(TE = hedges_g,
                 seTE = se,
                 studlab = study,
                 data = sim$data_aggr %>% filter(study <= 10),
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 title = "Meta-Analysis fixed-effect")

summary(metaanalysis)

```

# Forest plot
```{r}
forest(metaanalysis)

```

