---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# metafun

<!-- badges: start -->
<!-- badges: end -->

'metafun' offers valuable functions for teaching and understanding statistical concepts related to meta-analyses using a simulation-based approach. Please note that this package is currently under development, and full functionality is not yet available.

## Installation

You can install the development version of metafun from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("simschaefer/metafun")
```

Load package in R:
```{r}
require(metafun)
```

# Standardized Mean Differences

## Fixed Effect Model

### Simulate Data

Simulates data of multiple studies using predefined effect sizes and between study heterogenity ($\tau$).

```{r}
sim <- sim_meta(min_obs = 20,
         max_obs = 2000,
         n_studies = 1500,
         smd_true = 0.3,
         r_true = 0,
         random = FALSE,
         metaregression = FALSE)

head(sim)
```

### Effect size and standard error

```{r message=FALSE}
require(tidyverse)

ggplot(sim, aes(x = hedges_g, y = log(se_g), color = n1))+
  geom_point(alpha = 0.5)+
  theme_minimal()+
  labs(x = "Effect Size (ES)",
       y = "log(SE)")+
  scale_color_viridis_c()
```

### Run Meta-Analysis on simulated data

```{r message=FALSE}
require(meta)

#select only studies 1-10 for better readability
sim <- sim %>% 
  filter(study <= 10)

meta_fixed <- metagen(TE = hedges_g,
                 seTE = se_g,
                 studlab = study,
                 data = sim,
                 sm = "SMD",
                 fixed = TRUE,
                 random = FALSE,
                 title = "Meta-Analysis Fixed effect")

summary(meta_fixed)

```


### Forest plot
```{r fig.width=10, fig.height=5}
metafor::forest(meta_fixed,
             prediction = TRUE, 
             print.tau2 = TRUE,
             leftlabs = c("Study", "g", "SE"))

```


## Random-Effects model Standardized Mean Difference

### Simulate Data

```{r}
sim <- sim_meta(min_obs = 200,
         max_obs = 2000,
         n_studies = 10,
         smd_true = 0.7,
         random = TRUE,
         random_effects = c('SMD'),
         tau = 0.05)

head(sim)
```

### Run Meta-Analysis on simulated data

```{r fig.width=10, fig.height=5, message=FALSE}
require(meta)
require(metafor)

meta_random <- metagen(TE = hedges_g,
                 seTE = se_g,
                 studlab = study,
                 data = sim,
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = 'REML',
                 method.random.ci = "HK",
                 title = "Meta-Analysis Random Effects")

summary(meta_random)


metafor::forest(meta_random,
             prediction = TRUE, 
             print.tau2 = TRUE,
             leftlabs = c("Study", "g", "SE"))
```

# Correlations

## Fixed Effect Model

### Simulate data

Simulates data of multiple studies using predefined effect sizes and between study heterogenity ($\tau$).

```{r}
sim <- sim_meta(min_obs = 200,
         max_obs = 2000,
         n_studies = 10,
         smd_true = 0,
         r_true = 0.5,
         random = FALSE)

head(sim)
```
### Run Meta-Analysis on simulated data

```{r message=FALSE}
require(meta)

meta_fixed <- metagen(TE = z,
                 seTE = se_z,
                 studlab = study,
                 data = sim,
                 sm = "ZCOR",
                 fixed = TRUE,
                 random = FALSE,
                 title = "Meta-Analysis Fixed effect")

summary(meta_fixed)

```

### Forest plot
```{r fig.width=10, fig.height=5}
metafor::forest(meta_fixed,
             prediction = TRUE, 
             print.tau2 = TRUE,
             leftlabs = c("Study", "r", "SE"))

```

## Random Effects Model

### Simulate data

```{r}
sim <- sim_meta(min_obs = 200,
         max_obs = 2000,
         n_studies = 10,
         smd_true = 0,
         r_true = 0.5,
         random = TRUE,
         random_effects = c('ZCOR'),
         tau = 0.1)

head(sim)
```

### Run Meta-Analysis on simulated data

```{r fig.width=10, fig.height=5, message=FALSE}

meta_random <- metagen(TE = z,
                 seTE = se_z,
                 studlab = study,
                 data = sim,
                 sm = "ZCOR",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = 'REML',
                 method.random.ci = "HK",
                 title = "Meta-Analysis Random Effects")

summary(meta_random)


metafor::forest(meta_random,
             prediction = TRUE, 
             print.tau2 = TRUE,
             leftlabs = c("Study", "r", "SE"))
```

# Subgroup-Analysis Standardized Mean Difference

### Simulate Data

```{r}
sim <- sim_meta(min_obs = 200,
         max_obs = 2000,
         n_studies = 30,
         smd_true = 0.2,
         r_true = 0,
         random = TRUE,
         tau = 0.1,
         random_effects = c('SMD'),
         metaregression = TRUE,
         smd_mod_effects = c(0.1,0.2,0.3),
         r_mod_effects = c(0,0,0),
         mod_labels = c('group1', 'group2', 'group3'))

head(sim %>% 
       select(study, hedges_g, subgroups, everything()))
```

### Run Meta-Analysis on simulated data

```{r fig.width=10, fig.height=12, message=FALSE}
meta_random <- metagen(TE = hedges_g,
                 seTE = se_g,
                 studlab = study,
                 data = sim,
                 sm = "SMD",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = 'REML',
                 method.random.ci = "HK",
                 subgroup = subgroups,
                 title = "Meta-Analysis Random Effects")

summary(meta_random)


metafor::forest(meta_random,
             prediction = TRUE, 
             print.tau2 = TRUE,
             leftlabs = c("Study", "g", "SE"))
```

# Metaregression

## Simulate Data
```{r}

# define values of moderator variable:
x <- 1:100/100

# define slope:
b <- -0.5

df <- sim_meta(min_obs = 1000,
               max_obs = 2000,
               n_studies = 30,
               smd_true = 0,
               r_true = 0,
               random = TRUE,
               tau = 0.1,
               random_effects = c('SMD'),
               metaregression = TRUE,
               mod_name = 'moderator',
               smd_mod_effects = b*x,
               r_mod_effects = rep(0,100),
               mod_labels = x)

# show correlation between moderator and effect size
ggplot(df, aes(moderator,hedges_g))+
  geom_point()+
  geom_smooth(method = 'lm')

mg <- metagen(TE = hedges_g,
              seTE = se_g,
              studlab = study,
              data = df,
              sm = "SMD",
              fixed = FALSE,
              random = TRUE,
              method.tau = 'REML',
              title = "Meta-Analysis fixed-effect",
              tau.common = FALSE)

m.gen.reg <- metareg(mg, ~moderator)

summary(m.gen.reg)

bubble(m.gen.reg, studlab = TRUE)

```

