---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# metafun

<!-- badges: start -->
<!-- badges: end -->

metafun provides useful functions to teach and understand statistical concept related to Meta-Analyses.

## Installation

You can install the development version of metafun from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("simschaefer/metafun")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(metafun)
## basic example code
```

## sim_meta

Simulates data of multiple studies using predefined effect sizes and between study heterogenity ($\tau$).

```{r}
df <- sim_meta(min_obs = 200,
         max_obs = 800,
         n_studies = 150,
         es_true = 0.7,
         es = 'SMD',
         fixed = TRUE,
         random = FALSE,
         varnames = c('x', 'y'))

head(df$data_aggr)
```

